The \kepler Smear Campaign I: An Asteroseismic Catalogue of Bright Red Giants

### 2018-12-05 paper/ms.tex
vsa revisions and duplicated references

% Beyond searching for planets, 
\kepler has revolutionized the field of asteroseismology both for solar-like oscillations \citep{2010PASP..122..131G,2010ApJ...713L.169C} and for coherent heat-engine driven oscillations \citep{2018arXiv180907779A}. It has yielded the detection of gravity-dominated mixed mode period spacings for red giants \citep{rggmodes,2014A&A...572L...5M}, enabling probes of interior rotation \citep{rggmoderotation,2012A&A...548A..10M,2012ApJ...756...19D} and distinguishing between hydrogen- and helium-burning cores \citep{rggmodehelium,2012A&A...540A.143M}. It has also permitted the determination of ages and fundamental parameters of cool main-sequence stars \citep{silvaages}, including planet-hosting stars \citep{huberplanetages,silvaplanetages,2016MNRAS.456.2183D,2018MNRAS.479.4786V}. \kepler gravity-mode asteroseismology has also been used to derive the internal rotation profiles of intermediate mass stars \citep{2015ApJ...810...16T,2018A&A...618A..24V}. %revealing the most ancient known planetary system, dating back to the earliest stages of the galaxy \citep{ancientplanets}. %By comparing asteroseismic stellar ages to stellar rotation periods, \citet{angusgyro} have shown that gyrochronology models cannot fit the data with a single relation, leading~\citet{vansadersgyro}~to suggest a qualitative change in dynamo mechanism as stars age through the main-sequence. 
\newpage

A major outcome of the \kepler asteroseismology programme is a legacy sample of extremely well characterized stars that can serve as benchmarks for future work \citep{keplerlegacy1,keplerlegacy2,silvaplanetages,2016MNRAS.456.2183D}. Asteroseismological studies with \kepler complement other probes of stellar physics well: for example, the APOKASC sample of~1916 spectroscopically- and asteroseismically-characterized red giant stars \citep{2014ApJS..215...19P}. For this APOKASC sample, \citet{hawkinsapogee} have been able to extract precise elemental abundances by fitting spectroscopic data with \logg and \teff fixed to asteroseismically-determined values. It is necessary to calibrate such a study against benchmark stars with very precisely-determined parameters, which in practice requires nearby bright stars that are amenable to very high signal-to-noise spectroscopy plus asteroseismology \citep{creeveybenchmark}, parallaxes \citep{hawkinsbenchmarks}, and/or interferometry \citep{casagrandebenchmark,creeveybenchmark2}. This is especially important in the context of the \gaia mission \citep{gaia}, which has recently put out its second data release of 1,692,919,135 sources, including 1,331,909,727 with parallaxes \citep{gaiadr2}. These data will form the basis of many large surveys and it is vital that they are calibrated correctly. To this end, 36~FGK stars including both giants and dwarfs have been chosen as \gaia benchmark stars for which metallicities \citep{gaiabenchmark1,2018RNAAS...2c.152J}, effective temperatures and asteroseismic surface gravities \citep{gaiabenchmark3}, and relative abundances of $\alpha$ and iron-peak elements \citep{gaiabenchmark4} have been determined. This includes only four main-sequence stars much cooler than the Sun, due to the paucity of such stars with asteroseismology. This has been accompanied by the release of high resolution spectra \citep{gaiabenchmark2} and formed the basis of extensions to lower metallicities \citep{gaiabenchmark5}, stellar twin studies \citep{gaiabenchmarktwins} and comparisons of stellar abundance determination pipelines \citep{gaiabenchmarkabundances}. Furthermore, by combining asteroseismology with optical interferometry, it has been possible to determine fundamental parameters of main-sequence and giant stars with unprecedented precision \citep{huber12,thetacygwhite,white15}.

>>>>

% Beyond searching for planets, 
\kepler has revolutionized the field of asteroseismology both for solar-like oscillations \citep{2010PASP..122..131G,2010ApJ...713L.169C} and for coherent heat-engine driven oscillations \citep{2018arXiv180907779A}. It has yielded the detection of gravity-dominated mixed mode period spacings for red giants \citep{rggmodes,2014A&A...572L...5M}, enabling probes of interior rotation \citep{rggmoderotation,2012A&A...548A..10M,2012ApJ...756...19D} and distinguishing between hydrogen- and helium-burning cores \citep{rggmodehelium,2012A&A...540A.143M}. It has also permitted the determination of ages and fundamental parameters of cool main-sequence stars \citep{silvaages}, including planet-hosting stars \citep{huberplanetages,silvaaguirre2015,2016MNRAS.456.2183D,2018MNRAS.479.4786V}. \kepler gravity-mode asteroseismology has also been used to derive the internal rotation profiles of intermediate mass stars \citep{triana15,vanreeth18}. %revealing the most ancient known planetary system, dating back to the earliest stages of the galaxy \citep{ancientplanets}. %By comparing asteroseismic stellar ages to stellar rotation periods, \citet{angusgyro} have shown that gyrochronology models cannot fit the data with a single relation, leading~\citet{vansadersgyro}~to suggest a qualitative change in dynamo mechanism as stars age through the main-sequence. 
\newpage

A major outcome of the \kepler asteroseismology programme is a legacy sample of extremely well characterized stars that can serve as benchmarks for future work \citep{keplerlegacy1,silvaaguirre2017,silvaaguirre2015,2016MNRAS.456.2183D}. Asteroseismological studies with \kepler complement other probes of stellar physics well: for example, the APOKASC sample of~1916 spectroscopically- and asteroseismically-characterized red giant stars \citep{2014ApJS..215...19P}. For this APOKASC sample, \citet{hawkinsapogee} have been able to extract precise elemental abundances by fitting spectroscopic data with \logg and \teff fixed to asteroseismically-determined values. It is necessary to calibrate such a study against benchmark stars with very precisely-determined parameters, which in practice requires nearby bright stars that are amenable to very high signal-to-noise spectroscopy plus asteroseismology \citep{creeveybenchmark}, parallaxes \citep{hawkinsbenchmarks}, and/or interferometry \citep{casagrandebenchmark,creeveybenchmark2}. This is especially important in the context of the \gaia mission \citep{gaia}, which has recently put out its second data release of 1,692,919,135 sources, including 1,331,909,727 with parallaxes \citep{gaiadr2}. These data will form the basis of many large surveys and it is vital that they are calibrated correctly. To this end, 36~FGK stars including both giants and dwarfs have been chosen as \gaia benchmark stars for which metallicities \citep{gaiabenchmark1,2018RNAAS...2c.152J}, effective temperatures and asteroseismic surface gravities \citep{gaiabenchmark3}, and relative abundances of $\alpha$ and iron-peak elements \citep{gaiabenchmark4} have been determined. This includes only four main-sequence stars much cooler than the Sun, due to the paucity of such stars with asteroseismology. This has been accompanied by the release of high resolution spectra \citep{gaiabenchmark2} and formed the basis of extensions to lower metallicities \citep{gaiabenchmark5}, stellar twin studies \citep{gaiabenchmarktwins} and comparisons of stellar abundance determination pipelines \citep{gaiabenchmarkabundances}. Furthermore, by combining asteroseismology with optical interferometry, it has been possible to determine fundamental parameters of main-sequence and giant stars with unprecedented precision \citep{huber12,thetacygwhite,white15}.
